---
title: "Shiny_Drake"
author: "Sean Wilson"
date: "24 June 2020"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r}
renderImage({
    list(src = "drake-equation-1600px.jpg",
         width = 1200)
  })
```
*Image from [SETI](https://www.seti.org/drake-equation-index) website*


## The Drake Equation

The Drake Equation is a statement that stimulates intellectual curiosity about the universe around us, for helping us to understand that life as we know it is the end product of a natural, cosmic evolution, and for helping us realize how much we are a part of that universe.  

N = R* x f(p) x n(e) x f(l) x f(i) x f(c) x L

N = Number of civilisations with which humans could communicate  
R* = mean rate of star formation in our galaxy
f(p) = fractions of stars that have planets  
n(e) = mean number of planets that could support life per star with planets  
f(l) = fraction of life-supporting planets that develop life  
f(i) = fraction of planets with life where life develops intelligence  
f(c) = fraction of intellegent civilisations that develop communication  
L = mean length of time that civilisations can communicate  

From Wikipedia:  
Criticism of the Drake equation follows mostly from the observation that several terms in the equation are largely or entirely based on conjecture. Star formation rates are well-known, and the incidence of planets has a sound theoretical and observational basis, but the other terms in the equation become very speculative. The uncertainties revolve around our understanding of the evolution of life, intelligence, and civilization, not physics. No statistical estimates are possible for some of the parameters, where only one example is known. The net result is that the equation cannot be used to draw firm conclusions of any kind, and the resulting margin of error is huge, far beyond what some consider acceptable or meaningful.

One reply to such criticisms is that even though the Drake equation currently involves speculation about unmeasured parameters, it was intended as a way to stimulate dialogue on these topics. Then the focus becomes how to proceed experimentally. Indeed, Drake originally formulated the equation **merely as an agenda for discussion** at the Green Bank conference.

```{r eruptions, echo=FALSE}
inputPanel(
  sliderInput("Rstar", label = "Mean rate of star formation in our galaxy:",
              min = 1, max = 5, value = 3, step = 0.5),
  
  sliderInput("fp", label = "Fraction of stars that have planets:",
              min = 0.1, max = 1, value = 1, step = 0.01),
  
  sliderInput("ne", label = "Mean number of planets that could support life per star with planets:",
              min = 0.2, max = 7, value = 1, step = 0.2),
  
  sliderInput("fl", label = "Fraction of the above that develop life:",
              min = 0.1, max = 7, value = 1, step = 0.2),
  
  sliderInput("fi", label = "Fraction of the above that develops intelligent life:",
              min = 0.01, max = 1, value = 0.5, step = 0.01),
  
  sliderInput("fc", label = "Fraction of the above that develop interstellar communication:",
              min = 0.01, max = 1, value = 0.1, step = 0.01),
  
  sliderInput("L", label = "Length of time civilisation remains communicating (thousand years): ", 
              min = 1, max = 1000, value = 10, step = 1)
)


renderText({
     paste0("These parameters estimate that there are ", 
                   round(input$Rstar * input$fp * input$ne * input$fl * input$fi * input$fc * input$L),
                   " civilisations that we could communicate with")
})

```










