---
title: "Shiny_Drake"
author: "Sean Wilson"
date: "24 June 2020"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r}
renderImage({
    list(src = "drake-equation-1600px.jpg",
         width = 1200)
  })
```
*Image from [SETI](https://www.seti.org/drake-equation-index) website*

## Are We Alone?

I'm sure it's a question that you've thought about at some point. Maybe you were looking up at the night sky, seeing twinkling lights showing the planets, stars and galaxies that surround us, or reading books, watching movies or TV shows with outer-space action, extra-terrestrial species, travelling through different planets around stars other than the Sun. I myself avidly remember seeing the reboot of Star Wars in the late 90s and falling in love with those movies, at which point I was exposed to the concept that we are one planet in a universe of stars, planets and moons and that maybe, other creatures are out there somewhere in the wide advances of space.


## What is The Drake Equation?

Studying science at university, I took an astrobiology unit which introduced me to "The Drake Equation". Lifted verbatim from the definition I googled:  
The Drake Equation is a statement that stimulates intellectual curiosity about the universe around us, for helping us to understand that life as we know it is the end product of a natural, cosmic evolution, and for helping us realize how much we are a part of that universe.  
Essentially, Frank Drake put forward a set of parameters that he thought could be used to get an idea of the number of civilisations we could expect to arise in the universe. He originally put the equation forward as a talking point, however since that original meeting the equation has been scrutinised, criticised and modified to try and shed light on that simple yet complex question: Are we alone?  

## The original equation  

Set out by Drake, the original equation was:  

N = R* x f(p) x n(e) x f(l) x f(i) x f(c) x L  
Where:  
N = Number of civilisations with which humans could communicate  
R* = mean rate of star formation in our galaxy
f(p) = fractions of stars that have planets  
n(e) = mean number of planets that could support life per star with planets  
f(l) = fraction of life-supporting planets that develop life  
f(i) = fraction of planets with life where life develops intelligence  
f(c) = fraction of intellegent civilisations that develop communication  
L = mean length of time that civilisations can communicate  

Summarising from [wikipedia](https://en.wikipedia.org/wiki/Drake_equation), the first couple of terms are fairly well understood from direct measurements. Star formation rates are seen to be between 1.5 and 3 per year, and we are improving our understanding of planet incidence arounds stars. Originally the figure was thought to be likely between 3-5, however other work has shown that perhaps 10% of star systems are hospitible to life. The next variable of planet/moon systems that could support life per star is another variable that we are learning about with the capacity to identify exoplanets improving. From this point, we are really making guestimates of the fraction of life supporting, intelligence and communicable species that will arise from these planets. Finally the length of time that a civilisation could communicate with us is important as we would need to have an overlapping period of time that this can occur.  

## So What's the Number?

With these parameters, there is a large range of potential outcomes from this equation. You can play with the parameters at each variable and see how this changes the output. Ranges are calculated to be within reasonably understood ranges for each of these. 

```{r eruptions, echo=FALSE}
inputPanel(
  sliderInput("Rstar", label = "Mean rate of star formation in our galaxy:",
              min = 1, max = 5, value = 3, step = 0.5),
  
  sliderInput("fp", label = "Fraction of stars that have planets:",
              min = 0.1, max = 1, value = 1, step = 0.01),
  
  sliderInput("ne", label = "Mean number of planets that could support life per star with planets:",
              min = 0.2, max = 7, value = 1, step = 0.2),
  
  sliderInput("fl", label = "Fraction of the above that develop life:",
              min = 0.1, max = 1, value = 1, step = 0.2),
  
  sliderInput("fi", label = "Fraction of the above that develops intelligent life:",
              min = 0.01, max = 1, value = 0.5, step = 0.01),
  
  sliderInput("fc", label = "Fraction of the above that develop interstellar communication:",
              min = 0.01, max = 1, value = 0.1, step = 0.01),
  
  sliderInput("L", label = "Length of time civilisation remains communicating (thousand years): ", 
              min = 1, max = 1000, value = 10, step = 1)
)


renderText({
     paste0("These parameters estimate that there are ", 
                   round(input$Rstar * input$fp * input$ne * input$fl * input$fi * input$fc * input$L),
                   " civilisations that we could communicate with")
})

```










